\subsection{Description}
Efficient framework system plays a key role in the services that Favendo offers to its customers and works as the enabler and customization point for consuming location based service. It consists of several related subsystems and goes by the project name Commander \cite{commanderfavendo}. Commander is executed with a highly available backend server side module that often securely hosts the classified information and a highly customizable mobile application SDK that is used to integrate location based services offered by Favendo to the mobile application developed for popular mobile software ecosystems such as iOS an Android. In order to provide the indoor navigation/positioning utility this framework comes with a map implementation customizable as per specific customer needs.

\par During my internship I was engaged with various enhancements and bug-fixes for this framework especially applicable for the iOS mobile platform. I have participated in the research and development efforts targeted towards the next major release of the commander mobile framework. I have learned a great deal about the iOS ecosystem in general and application programming constructs and relevant design patterns both with Swift and Objective-C as programming languages. I have participated in development efforts of reusable frameworks in the mobile application development. In the next sections I have provide a vivid summary of the subject matters that I have learned or closely dealt with and my reflection of the same. 