\section{Conclusion}
My motivation behind this internship was to have glimpse of how to take my programming skills to a professional level with applying the modern software development techniques while at the same time learning about location based services and Internet of Things based applications with hands on work experience. 
\par Location based services using Bluetooth Low Energy technology is becoming increasingly popular with only growing trends. But at the same time it has necessitated us to focus on the security and confidentiality aspects of  beacons technologies. HJ Tay et al. \cite{tay2016survey} have discussed in their work several vulnerabilities and possible attacks against the BLE beacon technologies such as spoofing, denial of service or hijacking with wide variety of real world consequences. They have also mentioned that currently extent of malicious attacks on such emerging technologies like iBeacons are limited because the variety of use cases for such emerging technologies are not so wide yet but situation is likely to change in coming few years. Nonetheless, beacon ranging is a promising technology with wide range of possibilities. With the foundational knowledge I have gained on the subject matter in my internship I now have scope to come up with more innovative solutions based on these technologies.
\par Moreover I have learned many best practices and techniques of professional software development like Test Driven Development or Object Oriented Design Patterns which are bound to improve my skills as a programmer. Since my work area was specialized on iOS platforms I have dealt with two programming languages namely Objective - C and its successor Swift. I have studied the API design guidelines and understood the significance of building reusable frameworks with both this languages and how to expose the relevant capabilities of such frameworks as APIs. This knowledge will come handy in all my relevant future endeavors on similar subject matters. I have concluded my internship with a rewarding working experience. 