\subsection{Real-world Applications}

\begin{itemize}
	\item \texttt{Rakete 7\cite{Rakete7}} [\url{https://www.rakete7.com}]
	
	Rakete 7 is a company based in Bamberg, Germany. It has played a crucial role in our mobility study behind the scene. Rakete 7 has adapted the concept of Physical Web and made a promising attempt to create a web environment for customers from the domains such as retail or tourism. In addition they are trying to provide value added service such as mobile payments or an effort to build a smart city in conjunction with the Internet of Things. 
	
	They use BLE beacons compliant with the EddyStone specification for their customers which can be deployed in distributed places and can be tracked with their client-side application \texttt{Substance\cite{Rakete7Substance}}[\url{https://substance.rakete7.com}]. Points of interest (POI) that are tagged with a beacon could link to useful content. E.g. a retail store could advertise a newly launched product, a museum could link to further information about an antique object on display. One such beacon kept in a retail store could act as a secure platform for mobile payments thus creating a seamless interaction between a customer and the store. Beacons scattered round the city could provide useful information to the visiting tourists.
	
	\item \texttt{Proxama\cite{Proxama}}  [\url{http://www.proxama.com}]
	
	Proxama PLC, proclaiming to be the UK's largest independent network of Bluetooth beacons,  is an international mobile commerce company operating across two divisions in proximity marketing via mobile and providing end-to-end solutions for card issuers to migrate customers from magnetic stripe credit and debit cards to mobile payments. With their services, they can deliver highly engaging content to consumer’s mobiles as they enter the proximity hot spot. It offers \texttt{TapPoint\cite{ProxamaTapPoint}}[\url{http://www.tappoint.com}] Mobile SDK and Platform which enables deployment of proximity marketing campaigns and enables consumer engagement both in on-line and off-line mode on various platforms.
	
	
	Proxama provides end-to-end support for cloud-based (HCE) payments and network/vendor payment models. Beacons placed across the city enriches the smart city environment by providing users location based informations e.g. bus schedules.
	
	\item \texttt{Aristotle Labs\cite{AristotleLabs}} [\url{http://aristotlelabs.aristotle.net}]
	
	Aristotle Labs is made of a team of developers based in Arkansas, creating  web applications  centered around user engagement. It creates practical Internet of Things solutions using beacon technology and uses data and design to provide  great user experiences for individual users and business.
	
	They have created a platform named \texttt{Beacon Sage\cite{BeaconSage}} [\url{https://www.beaconsage.com}] that creates new ways of displaying the property listing. It tries to engage the potential buyers with beautiful listing pages that are populated with multiple listing service data. Each property on sale can be equipped with beacons where beacons will be configured to emit the information about the property.
	
\end{itemize}
\pagebreak
